\cleardoublepage
\phantomsection
\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

Instant messaging applications are a major component of interpersonal communications; even more so for people who do not see each other on a day-to-day basis. In October 2020, WhatsApp reported sending about 200 billion messages per day \cite{whatsAppsPerDay} and, as of today, it has more than 2 billion users.\cite{whatsAppsUsers} Globally, in a second place according to application downloads \cite{telegramSecondPlaceGlobally}, Telegram has 700 million users who send more than 15 billion messages on daily basis. \cite{telegramMessagesPerDay}

According to Robin Dunbar, humans capacity to maintain active social relationships is limited.\cite{dunbarNumber} Knowing the objective state of personal relationships with our circles can be of vital importance for the maintenance, preservation and improvement of strong, lasting and healthy relationships.

The main objective of this project is to provide the user with a tool that offers this unbiased data in a visual and easily understandable way. This data can help users take actions to improve their interactions. We decided to name the tool: \textit{ChatStats}.

On the other hand, users are becoming increasingly aware of the value of their data and the possible negative uses of its collection. Privacy is a major concern in the realm of personal conversations, so it has been extensively considered during the development of this project. To protect user data, the entire application is sent to the client, where all necessary operations with conversations are performed locally.

In addition, \textit{ChatStats} is open source, allowing access to the code for reading and modification by users and contributors; under the \acrfull{gplv3} license. The application has been developed using React, an open source framework developed mainly by Facebook.

Overall, this project presents the design and implementation of a web application that allows users to analyze their WhatsApp or Telegram chats and gain insights into their social interactions and relationships, all while ensuring data privacy and accessibility under an open-source license.

\begin{comment}
	The use of instant messaging applications has become a vital component of interpersonal communication, especially for individuals who do not have the opportunity to interact on a daily basis. WhatsApp, one of the most popular instant messaging platforms, reported sending approximately 200 billion messages per day in October 2020, and currently has over 2 billion users.
	
	In 1992, Robin Dunbar proposed Dunbar's number, which approximates the number of people with whom an individual can maintain stable social relationships at around 150. Understanding the objective state of personal relationships within our social circles can be crucial for maintaining, preserving, and improving strong, lasting, and healthy relationships.
	
	This thesis presents the design and implementation of a web application that aims to provide users with a tool to analyze and understand their WhatsApp chats in a visual and easily comprehensible way. The application allows users to gain insights into their social interactions and relationships, taking into account Dunbar's number.
	
	Privacy is a major concern in the realm of personal conversations, and it has been considered a primary concern during the development of this application. To protect user data, the entire application is sent to the client, and all necessary operations are executed on the client's device. Additionally, the application is open-source, and the code is freely accessible for reading and modification by users and contributors under the \acrfull{gplv3} license.\cite{GPLv3} The application is built using React.
	
	Overall, this thesis presents the design and implementation of a web application that allows users to analyze their WhatsApp chats and gain insights into their social interactions and relationships, all while ensuring data privacy and accessibility under an open-source license.
\end{comment}

\vfill
\textbf{Keywords: instante messaging, web application, JavaScript, open-source software, WhatsApp, privacy, Dunbar's number.} 